---
title: "Case Study - NYC airbnb"
author: "Molly Martorella"
date: "10/8/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)

library(p8105.datasets)

data(nyc_airbnb)

```

Investigate the data:

```{r}

str(nyc_airbnb)

nyc_airbnb %>%
  count(room_type)


nyc_airbnb %>%
  count(neighbourhood_group)

```

Does rating vary by neighborhood, room type, or both?
How is price related to other variables? i.e. does the rating drive price?
Where are rentals located?
how do airbnb prices compare to local rent?
which neighborhood is most expensive and which is cheapest?
do hosts with multiple sites have higher prices or ratings?
is average length of stay related to neighborhood, price?

```{r}
#rating drive price?

nyc_airbnb %>% ggplot(aes(x = review_scores_location, y = price)) +
  geom_point() +
  theme_bw()

nyc_airbnb %>% filter(reviews_per_month > 1) %>% 
  ggplot(aes(x = review_scores_location, y = price)) +
  geom_point() +
  theme_bw()


#neighborhood and price:

nyc_airbnb %>% 
  mutate(neighbourhood = as.factor(neighbourhood)) %>% 
  filter(neighborhood_group == "Manhattan") %>% 
  mutate(neighborhood = fct_reorder(neighbourhood, price, na.rm = TRUE)) %>% 
  ggplot()


#another attempt:

price_neighborhood = nyc_airbnb %>%
 janitor::clean_names() %>%
 group_by(neighbourhood_group, room_type) %>%
 summarize(mean_price = mean(price))

```

```{r}

#rentals located?

location <- nyc_airbnb %>% 
  filter(reviews_per_month > 1) %>%
  group_by(neighbourhood_group) %>% 
  summarise(n = n())

location %>% ggplot(aes(x = neighbourhood_group, y = n)) +
  geom_col() +
  theme_bw()

```


```{r}

#highest median price

nyc_airbnb %>% 
  group_by(neighbourhood_group) %>% 
  summarize(med_price = median(price, na.rm = TRUE))


nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(med_price = median(price, na.rm = TRUE)) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = med_price
  )

```


```{r}

nyc_airbnb %>% 
  filter(neighbourhood_group == "Staten Island", room_type == "Shared room") %>% 
  view()

```


```{r}

nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )

```


```{r}
nyc_airbnb %>%
 group_by(neighbourhood_group, neighbourhood) %>%
 summarize(
   mean_price = mean(price, na.rm = TRUE), 
   mean_review = mean(review_scores_location, na.rm = TRUE)) %>% 
  ggplot(aes(x = mean_review, y = mean_price)) +
  geom_point() +
  facet_grid(~neighborhood_group)

```


```{r}

nyc_airbnb %>%
 ggplot(aes(x = lat, y = long, color = neighbourhood_group)) +
 geom_point()


nyc_airbnb %>%
  filter(neighbourhood_group == "Manhattan",
         price < 1000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.3) +
  facet_grid(~room_type)

```

leaflet:

```{r}

library(leaflet)

nyc_airbnb %>%
  filter(neighbourhood_group == "Manhattan",
         price > 2000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~ lat, ~ long)

nyc_airbnb %>%
  filter(neighbourhood_group == "Manhattan",
         price > 2000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~ lat, ~ long)

pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location)

nyc_airbnb %>%
  filter(neighbourhood_group == "Manhattan") %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~ lat, ~ long, radius = .1, color = ~pal(review_scores_location))

```

